\documentclass{article}

%------------------------------------------------------------------------------
%Packages
\usepackage{comment}
%\usepackage[francais]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}

%------------------------------------------------------------------------------

\title{Plee the Bear \\--- English version ---}
\author{Julien Jorge, Sébastien Angibaud}
\date{\today}

\begin{document}

%------------------------------------------------------------------------------

\maketitle
\newpage
\tableofcontents
\newpage
%------------------------------------------------------------------------------

%------------------------------------------------------------------------------

\section{Foreword}
Following people got the wonderful idea to collaborate to making of
this document, and therefore to basis of the game, by giving their
good ideas and interesting comments :

% keep alphabetical order of family names in this list
\begin{itemize}
\item Pierre Fradin,
\item Julien Lassalle,
\item Anthony Leroy,
\item Florian Massuyeau.
\end{itemize}

Special thanks to Antoine Brémaud for having translated this document
from french to english.

%------------------------------------------------------------------------------
\section{Scenario}
4 PM or so, Plee wakes up, tired. He has dreamed again about that
awesome period when he went across the entire world together with his
belle. He puts his leg in the honey pot... empty! Moreover every
single honey pot in the house is empty. ``One more trick of that
kid'', he thinks. ``I'm going to give him such a wallop of which he
sure will remember''.

Following honey drops on the ground, Plee reaches the edge of the
forest. Beginning of the game.

%------------------------------------------------------------------------------
\section{Levels}
Other characters are possible for transitions :
\begin{itemize}
\item Lemmings,
\item Jim, from Earthworm Jim,
\item Bomberman,
\item a duck from Duck Hunt,
\item Kong, from Donkey Kong Country,
\item a character of Street Of Rage,
\item Duke, from Duke Nukem,
\item one teenage mutant ninja turtle.
\end{itemize}

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Forest}
\subsubsection{Environment}
``This is far from being paradise on Earth. It's cold, obscure and
wet. Behind each tree is hidden a wicked creature about to leap. First
these wasps grubbiness's bombarding at sight ; a throw of darts as
from a machine-gun. Thereafter come woodpeckers which fall straight on
you when coming to close. In case that you are a bit in a bad day, you
will certainly come nose to nose with a sow and its piglets. These
little devils then would do anything to get you falling down. And what
is to be found in a forest? Insects : ants with massive mandibles,
spiders as big as a man.''

\subsubsection{The boss}
The son's super hero (a giant racoon).
After the boss' defeat, the kid is seen entering a castle.

\subsubsection{Transition}
Meeting Belmont, the guy from Castelvania. Belmont gives a blow of
whip towards Plee, whom catches it. Plee pulls briskly on the
whip. Belmont falls to ground. Plee goes away tramping brutally on
him.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{The castle}
\subsubsection{Environment}
``This castle seems perfectly abandoned. It is wet and full of dust ;
only good to get demolished. Formerly occupied by a couple of amateurs
magicians, one has not seen whoever there for a few centuries. Like
any abandoned castle there's a legend behind. About this one is said
that, by one night of storm, the owners would have disputed. A few
weeks later they separated and none of them wanted to recover the
castle. Since that time it is forsaken. It is said that the devil
would have benefited form the occasion to settle there. He would
supervise the places using an army of skeletons, fallen souls and
other tricks to be found. But well, with me those skeletons will not
make old bones...''

About monsters one can take inspiration from any creatures of games
such as Diablo. For instance skeletons, spectre (ghosts), dead-alive
type ghouls, gargoyles.

There's in this castle a room with a single light source, where a
shadow effect should be made. In that room Plee could gain the power
to transform himself in a polar bear.

Ghosts are not killable enemies. There will be two kinds of ghosts ;
those that gather around Plee to reduce visibility and those that take
possession of Plee.  For the last ones, there will again be two
categories. Some will only change the keys configurations, others will
make Plee doing anything.

There will be a room in the castle with an isolated ghost. If the
player lets himself have, he will have the possibility to pass through
a wall for attaining a secret room.

\subsubsection{The boss}
An ignited tiger. That's an endurance test. The tiger burns
progressively and ends up dying. He's sad to burn, therefore he
cries. The challenge consists in avoiding the small balls of fire
which emanate from him. His tears evaporate and create a cloud, which
emits lightning (dangerous for Plee). The tiger then dies, the rain
falls and extinguishes him. Ideally one would want to see the level
water to increase gradually. Plee could go up on decorations to
escape the rise from water (kind of floating objects).

\subsubsection{Transition}
Mario jumps everywhere doing ``Mario Mario!'' Plee shows him how
fluid are his animations. Mario cries and is eaten by Yoshi. Plee then
goes away.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Earth center}
\subsubsection{Environment}
``I remember that, when I was kid, dad used to bring me to the mine.
He brought me in the morning and returned to seek me the evening.
While I was working hard to break stones, this crafty one was being
gone from there around every pub. Fortunately I met there other kids
in the same case ; we helped each other between the three of us. There
was Bobby, whom once found himself under a crumbling, poor him was at
the wrong place at the wrong time, and there was Jimmy. This young imp
was spending his time causing crumblings with large blows of dynamite.
One day that he lit the thing, Bobby, downwards, shouted something at
him. He did not have time to react that the bomb had already
exploded. How idiots were these two. Worst it is than nobody else knew
where loads were placed. Then it became dangerous to stay there, well
I mean that it became even more dangerous... I did not wait until they
take a decision, I quit. They closed the mine one week later.''

The level is globally going downwards. There could be places
completely in half-light. The level could be a succession of caves and
tunnels. One would start in a rather wet environment, with black/blue
colors, with puddle pools, and one would finish in a hot environment,
with black/red colors, puddle pools of lava. If the technique allows
it, one trip in mine trolley would be welcome.

With regards to enemies, one will find bats, small imps (to keep a
link with the preceding level devil), multiworms (TN: one head at each
end) and moles.

\subsubsection{The boss}
The room has platforms in height on which the devil and Plee can go
up. The devil puts blows of his tail if one is too close and spits
``homing'' balls of fire when one is far. While falling down of the
platforms, the devil causes a small crumbling. Plee can collect some
of the fallen stones. The goal is to throw eighteen of them on the
devil (with a metamorphosis of the devil all 6 stones). If Plee has
the fire capacity, the stones instead increase the energy of the devil
(it is thus necessary to get rid of the capacity). The devil can get
lava to spout out from the ground, with a small piece of ground. Plee
can go up on this piece of ground to go up on the platforms in height.

\subsubsection{Transition}
A wall separates Plee and Lara Croft. Lara leaves her weapons, her
arms pass through the wall. Plee is astonished by that, he catches her
arms and draws violently. Lara is burst against the wall, the wall
breaks down. Plee then goes away.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{The mountain}
\subsubsection{Environment}
``I am freezing. Here is again a place in which I would like not to
delay me. First because I am freezing, then because it is one of the
most hostile area which I know about. One speaks about a monster which
would haunt the snow-covered summits and which would transform whoever
would approach into simple snack. If you want my opinion it's one more
of these stories invented by tired parents to get their kids to eat
any kind of disappointing food. This said, what I am sure about is
that one easily finds there some dahuts (TN: legendary/joke animal
mostly looking like a donkey, with left or right legs shorter than the
contralateral ones in order to be able to stand on big slopes where he
lives, so that if one calls him from behind, he tries to turn back and
fall down the slope not being stable anymore, which is the dahut hunt
classical method...), staggering saint-bernard (TN: to be sure, the dog
with small cask of rum) or spangled which spits you in the face (they
spit far away those idiots). Together with cracks and stalactites
falling right on one's muzzle, I say this to you, it is far from being
piece of pleasure.''

The idea is to have an overall vertical progression. The level would
start in an environment a bit rocky, and would finish
snow-covered. One passes through caves with smooth walls which reflect
the character. One could even begin this level in a mine, to make a
transition from the preceding level; no matter because then the
preceding level would start and finish in a mine.

\paragraph{Design constraint :} in the caves with reflections there
should not be any non-decorative element other that Plee (he will be
the only one to be reflected).

\subsubsection{The boss}
Into a quite enlightened cave which reflects your littlest gesture and
where stalactites fall every ten seconds, a yeti has an annoying
tendency to attack you.

\subsubsection{Transition}
Link, the hero of the Zelda games, is playing with his sword. Plee
asks him why he has fun by throwing his sword in the air like
that. Link, distracted, plants it in his own foot. Plee then goes
away.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{The harbor}
\subsubsection{Environment}
``Damned harbor! It is necessary to pass from quays in boats while
avoiding some canon balls. From top of the masts, hordes of gulls
attack you. In bottom of holds, (another problem). Old loading cranes
make it possible to gain altitude, but beware of those which yield and
crush you. In the most dilapidated boats, it will be necessary to put
oneself to water. However if the boats frighten you, you still can try
to find a way via the sewers.''

First half of the level occurs on the quays, the second on the open
sea, on boats in single file (progression becomes very horizontal).

\subsubsection{The boss}
On a ship deck, it is about fighting against a phantom skeleton
pirate, his sword and his guns. Once the boss is killed, the boat
runs.

\subsubsection{Transition}
Ken, from ``Street Fighter'' which is as a fishmonger, irritated is
fighting against his own goods. Plee, famished, buys him fish (for
lack of honey). Plee then goes away.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Ocean}
\subsubsection{Environment}
``Pretty hard to breathe there. It is necessary to throw stones to
recover a bit of air (see~\ref{section-water}). About danger, there are
squids which throw ink, Naked-back knifefish which electrocute
anything they touch, without mentioning marine currents carrying you
towards famished sharks.''

\subsubsection{The boss}
A huge octopus with its eight tentacles. We must cut cutting them
all in once to win.

\subsubsection{Transition}
Ecco the dolphin lies on the ground until asphyxiating itself. Plee
then goes away.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Egypt}
\subsubsection{Environment}
``I'm hot. If you want to find some water points, some tombs will have
to be visited. If you visit a tomb, you are not sure to come out from
it. There are dangerous labyrinths. Moving sands, camels, stupid
mummies which whip you with their bandages.''

One could have a bar of Plee's dryness, and water points to reach to
refill it. If the bar is empty, one would lose energy gradually.

\subsubsection{The boss}
A sphinx with good breath and good claws.

\subsubsection{Transition}
Sonic makes a spin dash, directly toward Plee. Some peaks raise from
the ground and kill it. Plee then goes away.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{The sky}
\subsubsection{Environment}
This part of the game proceeds with an hot-air balloon. Kind of
``aerial'' level as there exists in many such games. Plee gives his
blows from inside the basket slung (technically feasible?). Enemies
could be birds with the malicious glance, pterodactyls, storm
clouds. One can imagine that it is necessary to recover gas bottles so
that the balloon continues to fly.

\textbf{Note (Julien) :} I am not fan of pterodactyls idea. As much as
the imaginary creatures are concerned it's fine for me, but the sudden
arrival of an anachronism disturbs me a bit.

\subsubsection{The boss}
God throwing lightnings, fallen angels (he tears off wings of angels
which pass by). The fallen angels are transformed into imps. The imps
attack God, the player must throw stones on God so that he cannot
avoid imps attacks.

\subsubsection{Transition}
Depending of next level existence:
\begin{itemize}
\item No transition, game over,
\item Joe Musashi, hero of Shinobi games suggests Plee to embark in a spaceship before stupidly falling into the vacuum.
\end{itemize}

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{The spaceship}
\subsubsection{Environment}
\textbf{This level is about to be deleted for it is ``mostly'' useless.}

Very metal, with sight on the universe. Enemies are robots. There are
moving walkways and, from time to time, electrical grounds (justified
by cables which lie by ground).

\subsubsection{The boss}
One can have as a boss an alien like in Mel brook's
``Spaceballs''. Another solution would be to use that honest R2D2 (or
Yoda) to explode Plee.

\subsubsection{Transition}
Plee finally finds back the kid who repurchases honey for him in one
of the famous supermarkets Gerald Leblaire.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{The moon}
\subsubsection{Environment}
The moon is finally a hidden level whose entry remains to be placed in
one of the other levels. Among possibilities planned for the way to
reach this level, we have:
\begin{itemize}
\item To complete a level with a number of energy balls containing a
single figure (eg.~333, 44) and superior to 10. One can possibly add
the need for obtaining the same state on the clock (eg.~1min. \&
11sec., 5~min. \& 55~sec.),
\item To complete the last-but-one level having discovered all the
secret ways in preceding levels.
\end{itemize}

In this level, there's less gravity and decoration is
slighter. Nevertheless it remains a real level, we thus need enemies
and bonuses. For the enemies one can consider the following
difficulties:
\begin{itemize}
\item drops of meteorites,
\item some Spielberg's E.T. sending rays by their finger,
\item or many small beasts kind of ``Mars Attacks!'',
\item some dirty ugly and ridiculous small beasts kind of ``Starship troopers'',
\item either bottles of air to be found (bonuses) which make it
possible for Plee to refill an air tank which becomes exhausted with
time spent in the level,
\item or a limited amount of time to carry out the level under penalty
of asphyxia and thus death.
\end{itemize}

\subsubsection{The boss}
What about almost twin brothers Dupont(d) from ``Tintin'', who would
attack Plee with their long colored barb (looking like in the comic)?

\subsubsection{Transition}
``Doom'' game hero (texturing like in the first ``Doom'') tries to
kill Plee in his usual butchery way. Plee gives him a snap which kills
him and then goes away.

%------------------------------------------------------------------------------
\section{Gameplay}

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Dialogues, comic strip style}
Dialogues appear inside the shape of bubbles, as in a comic strip,
dialogues with the characters of the game as well as between players.

We display onomatopoeias from time to time, when Plee jumps,
strikes, hits himself. When he falls too quickly, a series of ``A'' of
decreasing size, followed by an exclamation point, goes from the top
of the screen towards Plee.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Anti cheating technology}
From the beginning of the first level, if the player makes U-turn and
falls into a hole, he founds a door which makes it possible to finish
the game. Obviously the end by this way will be meaningless.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Well deserved easy ways}
One could put some bonuses into the levels which, once the game
finished, would make it possible to have some cheat codes. Each bonus
would give one code. Kind:
\begin{itemize}
\item selection of level,
\item invincibility (ie. never dies, except falling into a hole),
\item infinite energy (to remain indefinitely polar bear),
\end{itemize}

Once again we can make a different end according to whether the player
finished the play by cheating or not.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Counting points}
Each enemy brings back points, which are even more significant if they
are killed in series (less than one second occurred since last enemy
killed). Let say 100, 200, 500, 1~000, 10~000. From 10~000, a small
text appears, saying ``butchery'', ``slaughter'', ``
double-slaughter'', ``carnage''.

A the end of each level one counts player's energy balls left. Each
ball brings back 100 points. If the level must be done within an
assigned time, the player gains all the more points the quicker he got
it. The player gains one life each 50~000 points. One also makes
calculation of the killed enemies, kind of 100 points by enemy and a
bonus of 50~000 if all the enemies of the level were killed.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Default end}
After the sequence, we display credits which introduce all the
participants, then a screen presenting the cheat codes owned so far.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Random ends}
\subsubsection{Game over}
\subsubsection{The player did cheat during the game}
\subsubsection{The player did not complete the adventure}

%------------------------------------------------------------------------------
\section{Gameplay two players mode}
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Camera and multi-player mode}
The camera is centered between the two players. If one player leaves
the screen, the camera is automatically centered on one of them,
randomly or alternatively. It is possible to force the camera on one
of the two players, which leaves the other abandoned. More precisely,
each player has the possibility of placing the camera on himself.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Data sharing}
Each player has his own meter of points, lives, ``continues''. When
one player dies, it reappears on the last ground which he met (full
width of the player) or, if it is technically too difficult (see
below), on the last checkpoint/safe-point met. It may be, then, that
he reappears far away from the other player.

If the player does not have lives any more, one offers him to use
continuous (without stopping the other player's game). If he does not
have continuous any more, that's the end of the game for him. The
other player can continue, when he will not have continuous any more
the true large screen ``Game Over'' will appear.

\paragraph{Technical difficulty:}
How and where to store and retrieve the last ground met? Attention
should be paid not to store, for example, a moving platform.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Activity zones}
In order not to block a player when he is out of screen, it is
necessary that we make a zone of activity around each
player. Attention should then be paid not to get the objects which are
in the intersection of the two zones to progress twice. The solution
considered is to recover all the objects of the two zones, to send the
whole to the class managing collisions or progressions, then launching
collisions (or progressions) tests.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Network}
For a network game, communicated information is:
\begin{itemize}
\item actions carried out by the local player,
\item a change of level.
\end{itemize}

The progression of one player is made only after the time that he
received the actions carried out by the other one.

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Ends of game}
The second player needs to appear in the end sequences, otherwise he
is likely to feel injured.

%------------------------------------------------------------------------------
\section{Saves}
\subsection{Storage}
To be stored each time the player finishes a sub-level:
\begin{itemize}
\item the number of players (1 or 2),
\item the level and corresponding sub-level,
\item the number of lives of each player,
\item the number of continuous of each player,
\item the number of points of each player,
\item additional capacity,
\item the number of found bonuses and cheat-codes.
\end{itemize}

\subsection{Presentation}
The screen allowing for choice of the save to be used has, for each
save, a small image of the corresponding level and all the saved
values, except perhaps the number of found bonuses and cheat-codes
(because it is an hidden functionality).

\paragraph{Optional:}
The player can choose, for a save, the level to which he wants to
start (preceding or equal to the one where his progression
stopped). In this case the auto saving do not have to save the level if
it is before the one which is already saved. On the other hand the
lives and all the other parameters are to be saved.

%------------------------------------------------------------------------------
\section{Characteristic of Plee}
\begin{itemize}
\item Plee has good claws,
\item Plee gives good slaps while going or with the stop. He makes
      somersaulting while running,
\item Plee makes jumps more or less high according to the power
      accumulated beforehand. An aura of light appears and increases as much
      as long as the key of jump is being pressed,
\item Plee jumps from wall to wall hanging with his claws,
\item Plee can throw objects (stones),
\item Plee can dig certain walls,
\item Plee runs quickly and on four legs,
\item Plee is transformed into super polar bear by unzipping his fur,
\item if Plee becomes super polar bear, Plee gives great very
      effective blows of claws.
\end{itemize}

%------------------------------------------------------------------------------

\section{Weapons and powers}
\subsection{Stones}
Plee can collect stones to increase his ammunition. They explode when
they achieve their goal and they are more powerful than the slaps or
the somersaults.

\subsection{Energy}
Energy balls are the energy of Plee. If Plee is touched while using a
capacity, he loses this capacity. If not it loses all his energy
balls. If he hasn't got any, he dies. If Plee has more than 50 energy
balls, he can become super polar bear. If Plee becomes super polar
bear, Plee attracts the balls of energy close to him.

\subsection{Swarms}
The swarms contain bonuses. There will be swarms of invincibility, of
energy, of stones. Capacities of the fists and stones are fire,
electricity and steel. These capacities are combinable.

%------------------------------------------------------------------------------
\section{Water}
\label{section-water}
Plee loses electric and fire capacities in water. He does not launch
the stones far away (lack of effect). But they break and make bubbles
of breathable air.

%------------------------------------------------------------------------------
\section{Bonus levels}
With lots of honey. Opening is hidden in a normal level.

\end{document}
